Part B-2

### 2025-05-10 msca-pf-part-b1-template.tex
feat: update text according to template

@@

Employers and/or founders should ensure that a person is clearly identified to
whom researchers can refer for the performance of their professional duties, and
should inform the researchers accordingly.

@@

\textbf{Supervision} is one of the crucial elements of successful research. Guiding,
supporting, directing, advising and mentoring are key factors for a researcher
to pursue his/her career path. In this context, all MSCA-funded projects are
encouraged to follow the recommendations outlined in the
\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}.

>>>>

    \footnotetext{\emph{Interdisciplinarity} means the integration of information,
    data, techniques, tools, perspectives, concepts or theories from two or
    more scientific disciplines.}

@@

Employers and/or funders should ensure that a person is clearly identified to
whom researchers can refer for the performance of their professional duties, and
should inform the researchers accordingly.

@@

\textbf{Supervision} is one of the crucial elements of successful research. Guiding,
supporting, directing, advising and mentoring are key factors for a researcher
to pursue his/her career path. In this context, all MSCA-funded projects are
encouraged to follow the recommendations outlined in the
\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}
\footnotemark{}.

\footnotetext{While the MSCA Guidelines on Supervision are non-binding,
funded-projects are strongly encouraged to take them into account.}

### 2025-05-10 msca-pf-part-b2-template.tex
feat: bump year to 2025
feat: make font 12pt like template and update tags
feat: update text according to template

% NOTE: update these as necessary
% \mscaidentifier{HORIZON-MSCA-2024-PF-01}
% \mscaproject{TDB}

@@

Any information provided in Parts A and B of the proposal should be fully consistent.
Always mention full dates (using format: dd/mm/yyyy). The CV should include the
standard academic and research record. Any research career gaps and/or unconventional
paths should be clearly explained.

@@

\subsection{Template table: Overview of Participating Organisations}
\label{ssc:organisations:overview}
Only relevant rows from the table should be kept.

\begin{mscaorgoverview}
Beneficiary &
&
&
&
& \\
\hline
Associated partner linked to a beneficiary (if applicable) &
&
&
&
& \\
\hline
Associated partner for outgoing phase (mandatory for GF) &
&
&
&
& \\
\hline
Associated partner for secondment (optional) &
&
&
&
& \\
\hline
Associated partner for non-academic placement (optional) &
&
&
&
& \\
\hline
Other &
&
&
&
& \\
\hline
\end{mscaorgoverview}

@@

\begin{itemize}
    \item Beneficiary (compulsory).
    \item Associated partner linked to a beneficiary (if applicable)
    \item Associated partner for outgoing phase (compulsory for GF only)
    \item Associated partner for secondment (optional)
    \item Associated partner for non-academic placement (optional)
\end{itemize}

@@

Note that the expert evaluators will be instructed to disregard the contribution
of any associated partners for which no such evidence of commitment is submitted.

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-2024-PF, should the proposal be funded.

>>>>

% NOTE: update these as necessary
% \mscaidentifier{HORIZON-MSCA-2025-PF-01}
% \mscaproject{TDB}

@@

Any information provided in Parts A and B of the proposal should be fully consistent.
Always mention full consecutive dates (using format: dd/mm/yyyy). The CV should
include the standard academic and research record. Any research career gaps
and/or unconventional paths should be clearly explained and the dates must match
the ones provided in Part A (if applicable).

@@

\subsection{Template table: Overview of Participating Organisations}
\label{ssc:organisations:overview}

Only relevant rows from the table should be kept.

\begin{mscaorgoverview}
Beneficiary &
&
&
&
& \\
\hline
Associated partner linked to a beneficiary (if applicable) &
&
&
&
& \\
\hline
Associated partner for outgoing phase (mandatory for GF) &
&
&
&
& \\
\hline
Associated partner for secondment (if applicable) &
&
&
&
& \\
\hline
Associated partner for non-academic placement (if applicable) &
&
&
&
& \\
\hline
\end{mscaorgoverview}

@@

\begin{itemize}
    \item Beneficiary (compulsory).
    \item Associated partner linked to a beneficiary (if applicable)
    \item Associated partner for outgoing phase (compulsory for GF only)
    \item Associated partner for secondment (if applicable)
    \item Associated partner for non-academic placement (if applicable)
\end{itemize}

@@

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-2025-PF, should the proposal be funded.
